---
title: "R03_2_InClass_scraping_dcard"
author: "Jilung Hsieh"
date: "2019/9/2"
output:
  html_document:
    highlight: zenburn
    number_sections: yes
    theme: cerulean
    toc: yes
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Loading library
```{r}
library(tidyverse)
library(httr)
library(jsonlite)
options(stringsAsFactors = F)
```



# Inspecting one dcard url using Chrome DevelopTools
- Inspecting the page by right-click mouse
- Reloading the page and try to find the JSON file storing post data
- Clicking tab "latest" to see what happened

```{r}
url_dcard <- "https://www.dcard.tw/f/relationship"
browseURL(url_dcard)
```



# Finding out url rules

## Finding out the url rule by 3 pages data
- Getting back 3 pages data
- However, No url rule was found by observing urls directedly.

```{r}
url1 <- "https://www.dcard.tw/_api/forums/relationship/posts?popular=false&limit=30"
url2 <- "https://www.dcard.tw/_api/forums/relationship/posts?popular=false&limit=30&before=232231641"
url3 <- "https://www.dcard.tw/_api/forums/relationship/posts?popular=false&limit=30&before=232230790"
```


## Getting them back and previewing them
Previewing data to find out url rules inside data. **IT MUST** have some rules to know the next url.

```{r}
res1 <- GET(url1) %>% content("text") %>% fromJSON()
res2 <- GET(url2) %>% content("text") %>% fromJSON()
res3 <- GET(url3) %>% content("text") %>% fromJSON()
```

## ANS: Printing out the 30th post id of each page data 
The 30th post id is part of the url of next chunk data
```{r}
res1$id[30]
url2
res2$id[30]
url3
res3$id[30]
```

# Step-by-Step code

## Getting the first page
```{r}
url <- "https://www.dcard.tw/_api/forums/relationship/posts?popular=false&limit=30"
res <- GET(url) %>% content("text") %>% fromJSON()  %>%
        select(-tags, -topics, -mediaMeta, -reactions, -media, -meta, -customStyle)
```

## get the next chunk of data
```{r}
next_url <- paste0("https://www.dcard.tw/_api/forums/relationship/posts?popular=false&limit=30&before=", res$id[30])
res <- GET(next_url) %>% content("text") %>% fromJSON() %>%
        select(-tags, -topics, -mediaMeta, -reactions, -media, -meta, -customStyle)
```


## Using for-loop to getting more data

```{r}
for(i in 1:5){
    next_url <- paste0("https://www.dcard.tw/_api/forums/relationship/posts?popular=false&limit=30&before=", res$id[30])
    res <- GET(next_url) %>% content("text") %>% fromJSON() %>%
        select(-tags, -topics, -mediaMeta, -reactions, -media, -meta, -customStyle)
    print(next_url)
}
```


## Assigning the 1st data.frame res to post.df to collect all data
```{r}
url <- "https://www.dcard.tw/_api/forums/relationship/posts?popular=false&limit=30"
res <- GET(url) %>% content("text") %>% fromJSON()  %>%
        select(-tags, -topics, -mediaMeta, -reactions, -media, -meta, -customStyle)
post.df <- res
```


## Using for-loop to get more data and bind to the end of post.df
```{r}
for(i in 1:5){
    next_url <- paste0("https://www.dcard.tw/_api/forums/relationship/posts?popular=false&limit=30&before=", res$id[30])
    res <- GET(next_url) %>% content("text") %>% fromJSON() %>%
        select(-tags, -topics, -mediaMeta, -reactions, -media, -meta, -customStyle)
    glimpse(res)
    post.df <- bind_rows(post.df %>% select(id, title), res %>% select(id, title))
    print(next_url)
    print(nrow(post.df))
}

```

# Full code
- Assigning a big enough i to for-loop
- Let error occurs to know which url is the ending url3
```{r}
url <- "https://www.dcard.tw/_api/forums/relationship/posts?popular=false&limit=30"

res <- GET(url) %>% content("text") %>% fromJSON()  %>%
        select(-tags, -topics, -mediaMeta, -reactions, -media, -meta, -customStyle)

post.df <- res

for(i in 1:500){
    next_url <- paste0(url, "&before=", res$id[30])
    res <- GET(next_url) %>% content("text") %>% fromJSON() %>%
        select(-tags, -topics, -mediaMeta, -reactions, -media, -meta, -customStyle)
    post.df <- bind_rows(post.df, res)
    message("[", i, "] ", nrow(post.df))
}

# Error: lexical error: invalid char in json text.
#                                        <!DOCTYPE html> <!--[if lt IE 7
#                      (right here) ------^

```

## print out the ending url
```{r}
print(next_url)
res %>% glimpse()
```

